Aldebaran~b's temperate past uncovered in planet search data

### 2018-07-11 paper/aldebaran.tex
Closes #8
Mention SONG in abstract.

\begin{abstract}
The nearby red giant Aldebaran is known to host a gas giant planetary companion from decades of ground-based spectroscopic radial velocity measurements. Using Gaussian Process-based Continuous Auto-Regressive Moving Average (CARMA) models, we show that these historic data also contain evidence of acoustic oscillations in the star itself, and verify this result with further dedicated ground-based spectroscopy and space-based photometry with the \kepler Space Telescope. From the frequency of these oscillations we determine the mass of Aldebaran to be $1.16 \pm 0.07$~\msun, and note that this implies its planet will have been subject to insolation comparable to the Earth for some of the star's main sequence lifetime. Our approach to sparse, irregularly sampled time series astronomical observations has the potential to unlock asteroseismic measurements for thousands of stars in archival data, and push to lower-mass planets around red giant stars.
\end{abstract}

>>>>

\begin{abstract} The nearby red giant Aldebaran is known to host a gas giant
planetary companion from decades of ground-based spectroscopic radial velocity
measurements. Using Gaussian Process-based Continuous Auto-Regressive Moving
Average (CARMA) models, we show that these historic data also contain evidence
of acoustic oscillations in the star itself, and verify this result with further
dedicated ground-based spectroscopy using the SONG telescope and space-based
photometry with the \kepler Space Telescope. From the frequency of these
oscillations we determine the mass of Aldebaran to be $1.16 \pm 0.07$~\msun, and
note that this implies its planet will have been subject to insolation
comparable to the Earth for some of the star's main sequence lifetime. Our
approach to sparse, irregularly sampled time series astronomical observations
has the potential to unlock asteroseismic measurements for thousands of stars in
archival data, and push to lower-mass planets around red giant stars.
\end{abstract}
